Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-14 chapters/introduction/introduction.tex
add citations

\subsection{Deep Learning in Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.

@@

Automatic feature engineering has drawn a lot of attention over the
past years in the computer vision community due to its efficiency and
not requiring expert knowledge about the data. Deep neural networks
are wildly accepted by researchers as good tools to learn high-level
image representations.
The most commonly used approach for deep image feature learning is
full supervision, which usually requires manually annotated data
\todo{citations}.
Though full supervision work well in many applications, there are
exponentially more image resources without manual annotations (cell
phone imagery, YouTube videos\etc), which show a huge potential for
visual feature learning.  In recent years, people start studying
various approaches to exploit those unlabeled data. 
%
Recent work has explored the use of self-supervision (sometimes
referred to as unsupervised learning or pretext tasks) for training
deep neural networks that capture useful visual
representations~\cite{doersch2015unsupervised,pathak2016context}. 
These methods typically
exploit some known quantity of the data (e.g., pixel color values) to
avoid expensive manual annotation. As a byproduct, a useful visual
representation is learned.
For example, Zhang et al.~\cite{zhang2016colorful} show how image
colorization (synthesizing colors for a grayscale image) is a powerful
pretext task for learning visual representations. Pathak et
al.~\cite{pathak2017learning} exploit low-level motion-based grouping
cues for unsupervised feature learning.  
%
As new learning technique address the lack of massive amounts of
labeled data, domain adaptation adapt the feature generating model to
another feature domain so that it improve the performance when dealing
with new input
data~\cite{fernando2013unsupervised,fernando2015joint,saenko2010adapting,wang2016actions,tinghui2016flow}.
Duan \etal~\cite{duan2012learning} proposed to learn a linear
projection to transfer from the source feature subspace to the target
subspace. Sohn \etal~\cite{sohn2017unsupervised} improved the
performance of video face recognition using an adversarial-based
approach to adapt the network to unlabled video imagery.

>>>>

\subsection{Deep Learning in Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great a help for
researchers to conquer the problems like geo-localization and camera
calibration.
Weyand and Kostrikov \etal~\cite{planet} propose a convolutional
network to predict the geographic location given an input
image.~\cite{walch2017image} applies LSTM on CNN features learned for
camera localization.

@@

Automatic feature engineering has drawn a lot of attention over the
past years in the computer vision community due to its efficiency and
not requiring expert knowledge about the data. Deep neural networks
are wildly accepted by researchers as good tools to learn high-level
image representations.
The most commonly used approach for deep image feature learning is
full supervision, which usually requires manually annotated
data~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
Though full supervision work well in many applications, there are
exponentially more image resources without manual annotations (cell
phone imagery, YouTube videos\etc), which show a huge potential for
visual feature learning.  In recent years, people start studying
various approaches to exploit those unlabeled data. 
%
Recent work has explored the use of self-supervision (sometimes
referred to as unsupervised learning or pretext tasks) for training
deep neural networks that capture useful visual
representations~\cite{doersch2015unsupervised,pathak2016context}. 
These methods typically
exploit some known quantity of the data (e.g., pixel color values) to
avoid expensive manual annotation. As a byproduct, a useful visual
representation is learned.
For example, Zhang et al.~\cite{zhang2016colorful} show how image
colorization (synthesizing colors for a grayscale image) is a powerful
pretext task for learning visual representations. Pathak et
al.~\cite{pathak2017learning} exploit low-level motion-based grouping
cues for unsupervised feature learning.  
%
As new learning technique address the lack of massive amounts of
labeled data, domain adaptation adapt the feature generating model to
another feature domain so that it improve the performance when dealing
with new input
data~\cite{fernando2013unsupervised,fernando2015joint,saenko2010adapting,wang2016actions,tinghui2016flow}.
Duan \etal~\cite{duan2012learning} proposed to learn a linear
projection to transfer from the source feature subspace to the target
subspace. Sohn \etal~\cite{sohn2017unsupervised} improved the
performance of video face recognition using an adversarial-based
approach to adapt the network to unlabled video imagery.
